\documentclass[11pt,oneside]{article}\usepackage[]{graphicx}\usepackage[]{xcolor}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlsng}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hldef}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

% Minimal preamble (no font packages, no custom macros)
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}        % fine for pdfLaTeX; harmless for LuaLaTeX
\usepackage[utf8]{inputenc}     % ignored by LuaLaTeX; fine for pdfLaTeX
\usepackage{hyperref}           % keep links working

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

% ---- Header ----
{\LARGE \textbf{Nick Nassuphis}}\par
\rule{\textwidth}{0.5pt}

\small 28 Lancaster Gate, W2 3LP \hfill 07710462948; \href{mailto:nicknassuphis@gmail.com}{nicknassuphis@gmail.com}
\normalsize

\vspace{10pt}

% ---- Professional ----
\section*{Professional}

\textbf{ExodusPoint}, London, UK \hfill \emph{Sub Portfolio Manager: Sep 2020 -- May 2025}\par
\begin{itemize}
  \item Cross-asset volatility.
\end{itemize}

\textbf{Capstone Investment Advisors}, London, UK \hfill \emph{Portfolio Manager: Sep 2019 -- May 2020}\par
\begin{itemize}
  \item Cross-asset volatility.
\end{itemize}

\textbf{Insight Investment}, London, UK \hfill \emph{Senior PM, Absolute Insight: Apr 2017 -- May 2019}\par
\begin{itemize}
  \item Strategy analysis, development, benchmarking. Idea generation workflow. Investment process automation.
  New business development. Equity Long/Short, Cross-Asset Volatility, FX Overlay, Emerging Market Credit. Convertibles.
\end{itemize}

\textbf{CQS}, London, UK \hfill \emph{PM, Systematic strategies: Jan 2015 -- Mar 2017}\par
\begin{itemize}
  \item Alpha capture, systematic M\&A arbitrage, option overlays for equity long/short strategies,
  tactical asset allocation framework, risk analytics, idea generation workflow.
\end{itemize}

\textbf{North Harbour Capital / MapleLeaf Capital}, London, UK \hfill \emph{Managing Partner, Systematic strategies: Jan 2011 -- Dec 2014}\par
\begin{itemize}
  \item Systematic M\&A arbitrage, cross-asset trend following, equity factor strategies, analytics platform.
\end{itemize}

\textbf{Barclays Capital}, London, UK \hfill \emph{Head, Equity Exotic Derivatives Trading: May 2005 -- Jan 2011}\par
\begin{itemize}
  \item Responsible for 18 traders across London, New York, and Hong Kong.
  \item Managed the tail-risk mitigation portfolio for the equity exotics business.
\end{itemize}

\textbf{Credit Suisse}, London, UK \hfill \emph{MD, European Equity Exotic Derivatives: Feb 2000 -- Apr 2005}\par
\begin{itemize}
  \item Managing Director, responsible for single-stock, index, and equity hybrids from 2004.
  \item Director, responsible for the single-stock correlation business from 2000 onwards.
\end{itemize}

\textbf{WestLB}, London, UK \hfill \emph{Head, FX Exotic Derivatives: Jun 1997 -- Jan 2000}\par
\begin{itemize}
  \item Set up and managed the FX exotics business.
\end{itemize}

\textbf{Bankers Trust}, London, UK \hfill \emph{VP, European FX Exotic Derivatives: Aug 1994 -- May 1997}\par
\begin{itemize}
  \item Trader, FX exotics desk.
\end{itemize}

% ---- Education ----
\section*{Education}

\textbf{Massachusetts Institute of Technology}, Cambridge, MA \hfill \emph{1991 -- 1994}\par
\begin{itemize}
  \item MSc Engineering.
\end{itemize}

% ---- Other ----
\section*{Other}

\begin{itemize}
  \item Equity risk factor toolkit:
  \href{http://tinyurl.com/jhtcay3}{\texttt{tinyurl.com/jhtcay3}}
  \item Volatility and the Buyback Anomaly:
  \href{http://tinyurl.com/grevzzv}{\texttt{tinyurl.com/grevzzv}}
  \item Regularized Robust Portfolio Estimation:
  \href{https://tinyurl.com/3jh7y3b4}{\texttt{https://tinyurl.com/3jh7y3b4}}
  \item Domain-specific language for financial contracts:
  \href{http://tinyurl.com/639lf4f}{\texttt{tinyurl.com/639lf4f}}
  \item Angel investor, board member at a drug discovery startup:
  \href{https://www.reviral.co.uk/}{\texttt{https://www.reviral.co.uk/}}  
\end{itemize}

\end{document}
